\begin{spacing}{1}
\input{./lib/identitasabstrakEng.tex}	
%Tulis Abstrak disini
\textit{
  The Covid-19 pandemic that started in 2020 has been going on for 2 years. Although many people have received the vaccine, the government continues to emphasize the public to carry out health protocols especially in public places. Following the advice of WHO, one of the health protocols that need to be implemented is to keep a meter distance from each other. However, in implementing the health protocol, of course, many people tend to neglect the physical distancing practice. Therefore, a detection system that can help facilitate the implementation of health protocols especially physical distancing is needed. Crowd class is a class where there are 4 or more people within a 1 m radius, group class is a class where there are 2-3 people within a radius a meter while the person class is a class where there is only 1 person within a meter radius. This study utilizes the Mask-RCNN algorithm which is used to detect whether there is a crowd in an image taken. The objects detected in this study were divided into three classes, namely: Crowd, Group, and Person. The mask R-CNN algorithm detects objects by providing several object proposals which are then processed with the convolution layer and \emph{fully connected layer}. The output of the convolution layer is \emph{mask} which shows the image segmentation, while the output of \emph{fully connected layers} is to give the \emph{bounding box} and specify the class name of the object. The result of this study is a model that can detect crowds with an accuracy of 88.79\%
}

%Tulis Kata Kunci disini
\vspace{2ex}
\textbf{Keyword}: \emph{Mask R-CNN}, \emph{Crowd Detection}, \emph{Deep Learning}, \emph{Covid-19}.
\end{spacing}